### 2013-09-04 pystruct/paper.tex
better tables for library comparision

Using the formulation of structured prediction introduced in
\Secref{basics_structured_prediction}, learning can be broken down into three
sub-problems:
\begin{enumerate*}
    \item Encoding the structure of the problem in a joint feature function $\Phi$.
    \item Solving the loss-augmented prediction problem in Equation~\eqref{loss_augmentation}.
    \item Optimizing the objective \Eqref{learning_equation} with respect to $\theta$.
\end{enumerate*}
The first two problems are usually tightly coupled, as the maximization in
Equation~\ref{eq:main_equation} is usually only feasible by exploiting the
structure of $\Phi$, as described in \Secref{factor_graphs}. The last problem,
finding $\theta$, on the other hand, is usually treated as independent.
\pystruct takes an object-oriented approach to decouple the task-dependent
implementation of 2. and 3. from the general algorithms used to solve 1.

@@

Encoding the structure of the problem is done using \texttt{model} classes, which
compute $\Phi$ and encode the structure of the problem.
\pystruct implements models for many common cases, such as multi-class and
multi-label classification, conditional random fields with constant or
data-dependent pairwise potentials, and several latent variable models.
The maximization for finding $y$ in Equation~\ref{eq:main_equation} is carried out
using highly optimized implementations from external libraries. \pystruct
includes support for using {\sc OpenGM}~\citep{kappes2013comparative}, {\sc
LibDAI}~\citep{Mooij_libDAI_10}, QPBO fusion moves~\citep{rother2007optimizing},
and {\sc AD$^3$}~\citep{martins2011augmented}. It also includes an interface to
a general purpose linear programming solver from \textsc{cvxopt}~\cite{dahl2006cvxopt}.

Table~\ref{table:comparision} lists algorithms and models that are implemented
in \pystruct and compares them to other public structured prediction libraries,
together with the programming language and the project license.

\begin{table}[t]
\centering
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcccccccccc}
\toprule
Package &     Language &     License&\multicolumn{4}{c}{Algorithms}&\multicolumn{3}{c}{Models} \\
\cmidrule(r){1-1} \cmidrule(r){2-2} \cmidrule(r){3-3} \cmidrule(r){4-7} \cmidrule{8-10}
&             &&                     \footnotesize{CP}& \footnotesize{SG}& \footnotesize{LV}& \footnotesize{ML}& \footnotesize{Chain} & \footnotesize{Graph} & \footnotesize{LDCRF}\\
\pystruct&      Python &       BSD$^1$  & \x$^1$    & \x      & \x   & \o & \x     & \x     & \x \\
\svmstruct & C++ & non-free         & \x    & \o      & \x   & \o & \o     & \o     & \o \\
\sc{Dlib}         & C++        & boost            & \x    & \x      & \o   & \o & \x     & \x     &\o\\
\sc{CRFsuite}     & C++        & BSD              & \o    & \o      & \o   & \x & \x     & \o     &\o\\

\bottomrule
\end{tabularx}
    \caption{\label{table:comparision}Comparison of structured prediction
        software packages. CP stands for cutting plane optimization of
        SSVMs~\citep{joachims2009cutting}, SG for online subgradient
        optimization of SSVMs~\citep{ratliff2007online}, LV for latent variable
        SSVMs~\citep{yu2009learning}, ML for maximum likelihood learning, Chain
        for chain-structured models with pairwise interactions, Graph for
        arbitrary graphs with pairwise interactions, and LDCRF for latent
        dynamic CRF~\citep{morency2007latent}.  {\footnotesize $^1$\pystruct
        itself is BSD licensed, but uses the GPL-licensed package {\sc cvxopt}
    for cutting-plane learning.}
}
\end{table}
\vfill
\pagebreak

>>>>

\subsection{Library Structure and Content}
Using the formulation of structured prediction introduced in
\Secref{basics_structured_prediction}, learning can be broken down into three
sub-problems:
\begin{enumerate*}
    \item Encoding the structure of the problem in a joint feature function $\Phi$.
    \item Solving the loss-augmented prediction problem in Equation~\eqref{loss_augmentation}.
    \item Optimizing the objective \Eqref{learning_equation} with respect to $\theta$.
\end{enumerate*}
The first two problems are usually tightly coupled, as the maximization in
Equation~\ref{eq:main_equation} is usually only feasible by exploiting the
structure of $\Phi$, as described in \Secref{factor_graphs}. The last problem,
finding $\theta$, on the other hand, is usually treated as independent.
\pystruct takes an object-oriented approach to decouple the task-dependent
implementation of 2. and 3. from the general algorithms used to solve 1.

@@

Encoding the structure of the problem is done using \texttt{model} classes, which
compute $\Phi$ and encode the structure of the problem.
\pystruct implements models for many common cases, such as multi-class and
multi-label classification, conditional random fields with constant or
data-dependent pairwise potentials, and several latent variable models.

The maximization for finding $y$ in Equation~\ref{eq:main_equation} is carried out
using highly optimized implementations from external libraries. \pystruct
includes support for using {\sc OpenGM}~\citep{kappes2013comparative}, {\sc
LibDAI}~\citep{Mooij_libDAI_10}, QPBO fusion moves~\citep{rother2007optimizing},
and {\sc AD$^3$}~\citep{martins2011augmented}. It also includes an interface to
a general purpose linear programming solver from \textsc{cvxopt}~\cite{dahl2006cvxopt}.

Table~\ref{table:comparision_algorithms} lists learning algorithms that are implemented
in \pystruct and compares them to other public structured prediction libraries.
Table~\ref{table:comparision_models} lists

%TODO what about language / license?
\begin{table}[t]
\centering
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcccccc}
\toprule
Package       & Cutting Plane& SSGD & BCFW & Latent SSVM & Perceptron & ML\\
\cmidrule(r){1-1} \cmidrule(r){2-7}
\pystruct     & \x        & \x   & \x   & \x          & \x         & \o\\
\svmstruct    & \x        & \o   & \o   & \x          & \o         & \o\\
\sc{Dlib}     & \x        & \x   & \o   & \o          & \x         & \o\\
\sc{CRFsuite} & \o        & \o   & \o   & \o          & \x         & \x\\

\bottomrule
\end{tabularx}
    \caption{\label{table:comparision_algorithms}Comparison of learning
        algorithms implemented in popular structured prediction software
        packages. SSGD stochastic subgradient decent learning of SSVMs, BCFW for
    Block-Coordinate Frank-Wolfe, Latent SSVM for latent variable SSVMs, ML for
    maximum likelihood learning}
\end{table}

\begin{table}[t]
\centering
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcccccc}
\toprule
Package        &Multi-Class &  Multi-Label & Chain & Graph & LSVM  &LDCRF \\
\cmidrule(r){1-1} \cmidrule(r){2-7}
\pystruct      & \x         & \x           & \x    & \x    & \x    & \x    \\
\svmstruct     & \x         & \x           & \o    & \o    & \o    & \o    \\
\sc{Dlib}      & \x         & \o           & \x    & \x    & \o    & \o    \\
\sc{CRFsuite}  & \o         & \o           & \x    & \o    & \o    & \o    \\

\bottomrule
\end{tabularx}
    \caption{\label{table:comparision_models}Comparison of models implemented
    in popular structured prediction software packages. LSVM stands for the latent multi-class SVM, LDCRF for
    latend dynamic conditional random fields.}
\end{table}
